Online reprocessing simulation for thorium-fueled molten salt breeder reactor

### 2017-07-09 msbr_reproc.tex
reordering of wording and capturing more math in math mode.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Description of the actual work}
The \gls{MSBR} is a thermal spectrum reactor. The reactor vessel has a diameter of 
$680 cm$ and a height of $610 cm$. It contains a molten fluoride fuel-salt mixture 
which performs two functions: to generate heat in the moderated region and to 
transport heat energy from the core to primary heat exchanger using the primary 
salt pump. The vessel also contains graphite blocks for neutron moderation and 
reflection. The lithium in the fuel-salt solution is enriched to 99.995\% 
$^7$Li because $^6$Li is a very strong neutron poison and becomes tritium upon 
neutron bombardment. In this study, the 0.005\% atomic fraction of $^6$Li has 
been taken into account because even such a small amount of isotope with very 
high absorption cross section might significantly affect on neutron flux energy 
distribution and, consequently, on depletion calculation results. 
Table~\ref{tab:data} is the summary of the major \gls{MSBR} parameters 
\cite{robertson_conceptual_1971}.

@@

The \gls{MSBR} core consists of two different zones. The central 
zone, Zone I, in which 13.2\% of the volume is fuel salt and 86.8\% graphite. 
The first zone is composed of 1320 graphite cells, 2 graphite control rods, and 
2 safety rods consisting of boron carbide clad. The under-moderated zone, Zone 
II, with 37\% fuel salt, and radial reflector, surrounding the more active 
portion serves to diminish neutron leakage from the reactor core. In this work, 
only Zone I element with the hole diameter of 3.42138 cm, and the molten-salt 
fuel volume fraction is 0.132 was considered. Figure~\ref{fig:zoneI} shows the 
geometry of unit cell model. The boundary condition of the unit cell is 
periodic. The density of fuel salt is 3.3304 g/cm$^3$ and graphite one is 1.843 
g/cm$^3$. The temperature of fuel and graphite is fixed for the whole 
reprocessing cycle at 908K \cite{robertson_conceptual_1971}.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Description of the actual work}
The \gls{MSBR} is a thermal spectrum reactor. The reactor vessel has a diameter of 
$680 cm$ and a height of $610 cm$. It contains a molten fluoride fuel-salt mixture 
which performs two functions: to generate heat in the moderated region and to 
transport heat energy from the core to primary heat exchanger using the primary 
salt pump. The vessel also contains graphite blocks for neutron moderation and 
reflection. The lithium in the fuel-salt solution is enriched to 99.995\% 
$^7$Li because $^6$Li is a very strong neutron poison and becomes tritium upon 
neutron bombardment. In this study, the 0.005\% atomic fraction of $^6$Li has 
been taken into account because even such a small amount of isotope with very 
high absorption cross section can significantly impact the neutron flux energy 
distribution and, consequently, depletion calculation results. 
Table~\ref{tab:data} is the summary of the major \gls{MSBR} parameters used by 
this model \cite{robertson_conceptual_1971}.

@@

The \gls{MSBR} core consists of two different zones. The central 
zone, Zone I, in which 13.2\% of the volume is fuel salt and 86.8\% graphite. 
The first zone is composed of 1320 graphite cells, 2 graphite control rods, and 
2 safety rods consisting of boron carbide clad. The under-moderated zone, Zone 
II, with 37\% fuel salt, and radial reflector, surrounding the more active 
portion serves to diminish neutron leakage from the reactor core. In this work, 
only a Zone I element with a $3.42138 cm$ diameter central fuel channel and molten-salt 
fuel volume fraction of 0.132 was considered. Figure~\ref{fig:zoneI} shows the 
geometry of the unit cell model. The boundary condition of the unit cell is 
periodic. The density of the fuel salt is $3.3304 \frac{g}{cm^3}$ and the graphite density is 
$1.843 \frac{g}{cm^3}$. The temperature of fuel and graphite is fixed at 908K for the whole 
reprocessing cycle\cite{robertson_conceptual_1971}.
